Spfy: distributed predictive genomics of E.coli with graph based result linkage

### 2017-08-09 paper-webserver.tex
ADD: last of the outlines for methods/implementation
DEL: old outline
DEL: NAR filler text
ADD: some thoughts on the results/discussion paras
ADD: similar bioinfo platforms to compare to

\section{METHODS AND IMPLEMENTATION}
% outline
% para
% problem: predictive analylitcs in minutes - sol'n: RQ
%	related: packaging of modules in conda
% para (probably 2 paras)
% problem: distribute tasks & automate installation - sol'n: docker
% para(probably 2 for graphs)
% problem: storage up 10,000+ genomes - sol'n: graph database
% para
% problem: responsive ui that's easy to navigate - sol'n: react & material design
% shortpara
% problem: CI/testing - sol'n Github, TravisCI, Pytest

@@

\subsection{Graph databases and ontologies}
% para
% 1. spfy is built around graph technologies
% 2. graph dbs store data as a series of links
% 3. existing graph dbs and bioinformatics implementations
% para
% 1. how we structure our graph
% 2. ontoogies used
% 3. inferencing
% 3 1/2. SPARQL queries
% 4. results/timings

@@

\subsection{Real-time analysis pipelines}

@@

\subsubsection{}

\subsection{Task distribution and containerization}

@@

Docker integration ensures that software dependencies, which typically must be manually installed \cite{doi:10.1093/bioinformatics/btu153,laing2010pan,inouye2014srst2}, are handled automatically.

\subsection{Continuous integration and testing}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text
(see Figure \ref{NAR-fig1}).

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text.
\begin{equation*}
\mathrm{LD} \left( t \right) =
\sum\limits_i
a_i \exp \left( \frac{-t}{\tau_i} \right)
\end{equation*}
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text.

@@

\subsection{Guides and documentation}

@@

\subsection{Results subsection one}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text.

@@

\subsection{Results subsection two}

Text.  Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text (see Table \ref{table:01}).

Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text (see Figure \ref{NAR-fig2}a).

Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.

@@

\subsection{Results subsection three}

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text.

@@

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text.

@@

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text.

>>>>

\section{METHODS AND IMPLEMENTATION}
% para
% goals: predictive analylitcs in minutes, storage up 50,000-100,000 genomes

@@

\subsection{Graph databases and ontologies}
% para
% 0. Goals: big-data, everything linked, easy addition of new links
% 1. spfy is built around graph technologies
% 2. graph dbs store data as a series of links
% 3. existing graph dbs and bioinformatics implementations
% para
% 1. how we structure our graph
% 2. ontoogies used
% 3. inferencing
% 3 1/2. SPARQL queries
% 4. results/timings: scale

@@

\subsection{Real-time analysis pipelines and task distribution}
\subsection{Real-time analysis pipelines}
% para
% 1. goals: real-time, support for pipelines (linked modules)
% 2. how pipelines have been handled in the past: Galaxy, other examples
% 3. Python, RQ
% para
% 1. how we implemented RQ
%	related: packaging of modules in conda
% 2. different pipelines available
% 3. how pipelines are started from the front-end
% 4. result storage in graph db

@@

\subsubsection{Task distribution and parallelization}
% para
% 1. goals: scale analyses to "big-data", error handling
% 2. examples of different ways parallelization has been handled in the past
% 3. how we handle parallelization with RQ
% para
% 1. how many tasks have we tested this with
% 2. error handling: rq-dashboard, sentry
% 3. why options like sentry are better than traditional logging: scales well to tons (big-data levels) of tasks, groups the same errors together, reporting via email

\subsection{Containerization}
% para
% 1. goals: why compartmentilizations
% 2. examples of different virtualization technologies
% 3. intro do docker
% para
% 1. how we implemented docker
% 2. use of docker-compose
% 3. how this lets us replicate worker containers and link everything together

@@

Docker integration ensures that software dependencies, which typically must be manually installed \cite{doi:10.1093/bioinformatics/btu153,laing2010pan,inouye2014srst2,naccache2014cloud}, are handled automatically.

\subsection{Continuous integration and testing}
% para
% 1. goals: why CI, testing is important
% 2. examples of different testing platforms
% 3. how we've implemented it, integration with github

@@

\subsection{Guides and documentation}
% para
% 1. goals: use guide (ie. the README), dev guide
% 2. how docs have been done in the past (in general)
% 3. our use of ReadtheDocs

@@

\subsection{Further containerizing analyses modules}

% ex. in python, tox can be set to spin up docker containers for testing - see certbot
% could spin up a new container for each analysis module to run see \cite{di2015impact} - neglible performance impact

\subsection{Impact on Public Health Efforts}

% para
% focus on application

\subsection{Deployment to Cloud-Computing Platforms}
% how costs can be saved because using standard web tech means you can deploy to different cloud computing services

\subsection{Comparison with other bioinformatic pipeline technologies}

% namely galaxy

\subsection{Comparison with similar bioinformatic pipelines}

% para: \cite{naccache2014cloud}
% must install a ton of deps and even create dbs manually https://github.com/chiulab/surpi
% im not actually sure where they're getting the 'cloud-compatible' aspect of their paper from - its cloud compatible in that you deploy in the same manner as you would to bare-metal, but that's just like saying it 'runs on a computer'

% para: \cite{aanensen2016whole}
% makes some pretty pictures, but not really a pipeline

% para: \cite{joensen2014real,thomsen2016bacterial}
% we have a lot of similar directions to this, but just try to make it prettier, more friendly to use, and faster

@@

@@

@@

@@
